Wildcard: Spreadsheet-Driven Customization of Web Applications

### 2020-01-11 paper.tex
tweaks

\author{Geoffrey Litt}
\authorinfo{is a PhD student at MIT, researching programming tools for end users and developers.}
\author{Daniel Jackson}
\authorinfo{is a professor in the Department of Electrical Engineering and Computer Science at MIT, associate director of CSAIL, and a MacVicar Fellow. He leads the Software Design Group.}
\affiliation{Massachusetts Institute of Technology}

@@

To demonstrate the user experience of Wildcard, here is an example of
using it to help with booking a trip.{ These demos are best viewed as
videos in the online version of this paper
(\url{https://www.geoffreylitt.com/wildcard}).}

@@

\begin{itemize}
\tightlist
\item
  Wildcard aims support a broad set of customizations, but Sifter only
  supports sorting and filtering.
\item
  Wildcard shows the structured data table directly to the user. Sifter
  only shows sorting controls, and does not reveal the underlying data
  table.
\item
  Wildcard hides data extraction from end users. Sifter uses a
  combination of automated heuristics and interactive user feedback to
  involve end users in extracting data.
\end{itemize}

>>>>

\author{Geoffrey Litt}
\authorinfo{is a PhD student at MIT in the Software Design Group. His research focuses on programming tools, especially for live programming and end user programming.}
\author{Daniel Jackson}
\authorinfo{is a professor in the Department of Electrical Engineering and Computer Science at MIT, associate director of CSAIL, and a MacVicar Fellow. He leads the Software Design Group.}
\affiliation{Massachusetts Institute of Technology}

@@

To demonstrate the user experience of Wildcard, here's an example of
using it to help with booking a trip.{ These demos are best viewed as
videos in the online version of this paper
(\url{https://www.geoffreylitt.com/wildcard}).}

@@

\begin{itemize}
\tightlist
\item
  Wildcard supports a broad set of customizations, but Sifter only
  supports sorting and filtering.
\item
  Wildcard shows the structured data table directly to the user. Sifter
  only shows sorting controls, and does not reveal the underlying data
  table.
\item
  Wildcard hides data extraction from end users. Sifter uses a
  combination of automated heuristics and interactive user feedback to
  involve end users in extracting data.
\end{itemize}
